SPIRAL OPTIMIZATION ALGORITHM

### 2021-10-17 Semester I/Analisis Numerik Lanjut/Tugas Kerang/spiral.Rmd
no 1 done
tidur

>>>>

Saya coba _run_ sebanyak __100 kali__, berikut adalah rekap akar yang saya dapatkan:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
ceisya = data.frame()

for(i in 1:100){
  ahnaf = soa_mrf_2(N,a,b,a,b,rot,k_max,r)
  ceisya = rbind(ahnaf,ceisya)
}

ceisya %>% 
  mutate(x1 = round(x1,3),
         x2 = round(x2,3),
	 f = round(f,1)) %>% 
  distinct() %>%
  arrange(x1,x2)
```
